---
format:
  pdf:
    documentclass: ../MastersDoctoralThesis
    classoption: ["11pt", "english", "singlespacing", "headsepline"]
---

# Introduction {#sec-Chapter1}

## Main Section 1

![**CuAAC syntesväg.** schematisk figur som visar hur 3'ändan av en oligonukleotid märks in med en fluorophore. **a)** Panel a visar detta. **b)** Panel B visar detta.]



```{r echo=FALSE}
x <- rnorm(100, 30, 10) 
y <- rnorm(100, 5, 10)

mod1 <- t.test(x, y)

if(mod1$p.value < 0.0001){
    pvarde <- 0.0001
}else{
    pvarde <- mod1$p.value
}
```

Vi jämförde två grupper. Den första gruppen, _X_, hade större längd (_M_ = `r round(mean(x), 2)` cm, _SD_ = `r round(sd(x), 2)` cm) än den andra gruppen _Y_ (_M_ = `r round(mean(y), 2)` cm, _SD_ = `r round(sd(y), 2)` cm). Denna skillnad var också statistiskt säkerställd (_t_ = `r round(mod1$statistic, 2)`, _df_ `r round(mod1$parameter, 2)`= , _P_ < `r round(pvarde, 4)`).

## Cell densitet

Vi jämförde cell densitet.

```{r echo = FALSE, warning = FALSE, output = FALSE}
required_packages <- c("googlesheets4")
installed_packages <- installed.packages()
missing_packages <- setdiff(required_packages, installed_packages[, "Package"])

if (length(missing_packages) > 0) {
    install.packages(missing_packages)
}

# Load required libraries
library(googlesheets4)
googlesheets4::gs4_deauth()

spreadsheet_url <- "https://docs.google.com/spreadsheets/d/10r3DV5vFsZOu7DPbqlNHDd-WW0NrRXuFe8J5mhg-bQ8/edit?gid=0#gid=0"
sheet_name <- "Blad1"

# Read the data from Google Sheets
data <- read_sheet(spreadsheet_url, sheet = sheet_name)

#jämför 0.5 och 0.25
mod1 <- t.test(data$cell.density.cell.per.mL[data$dilution == 0.25], data$cell.density.cell.per.mL[data$dilution == 0.5] )

mod2 <- t.test(data$cell.density.cell.per.mL[data$dilution == 0.125], data$cell.density.cell.per.mL[data$dilution == 0.25] )

mod3 <- t.test(data$cell.density.cell.per.mL[data$dilution == 0.0625], data$cell.density.cell.per.mL[data$dilution == 0.125] )

```

Det var signifikant skillnad mellan 0.125 och 0.25 filution (_t_ = `r round(mod2$statistic, 2)`, _df_ `r round(mod2$parameter, 2)`= , _P_ = `r round(mod2$p.value, 2)`), men inte mellan 0.125 och 0.0625 (_t_ = `r round(mod3$statistic, 2)`, _df_ `r round(mod3$parameter, 2)`= , _P_ = `r round(mod3$p.value, 2)`)



## Welcome and Thank You

Welcome to this \LaTeX{} Thesis Template, using the \LaTeX{} typesetting system and [Quarto](quarto.org) and based on the \LaTeX{} thesis template MastersDoctoralThesis version 2.0 downloaded from [LaTeXTemplates](http://www.LaTeXTemplates.com). 
This LaTeX document class was authored by Vel (vel@latextemplates.com) and Johannes Böttcher based on a style file by Steve R. Gunn from the University of Southampton (UK), department of Electronics and Computer Science.


Det har visat sig i literaturen att formamid påverkar smälttemperaturen (Tm) av oligonukleotider [@blake_thermodynamic_1996; @fuchs_effects_2010].


## A Short Math Guide for \LaTeX{}

If you are writing a technical or mathematical thesis, then you may want to read the document by the AMS (American Mathematical Society) called, ``A Short Math Guide for \LaTeX{}". It can be found online at [AMS](http://www.ams.org/tex/amslatex.html) 
under the ``Additional Documentation" section towards the bottom of the page.

### Common \LaTeX{} Math Symbols

There are a multitude of mathematical symbols available for \LaTeX{} and it would take a great effort to learn the commands for them all. The most common ones you are likely to use are shown on [this page](http://www.sunilpatel.co.uk/latex-type/latex-math-symbols/).

You can use this page as a reference or crib sheet, the symbols are rendered as large, high quality images so you can quickly find the \LaTeX{} command for the symbol you need.


## About this Template

This \LaTeX{} Thesis Template is originally based and created around a \LaTeX{} style file created by Steve R. Gunn from the University of Southampton (UK), department of Electronics and Computer Science. You can find his original thesis style file at his site, here:
http://www.ecs.soton.ac.uk/~srg/softwaretools/document/templates/.

Steve's `ecsthesis.cls` was then taken by Sunil Patel who modified it by creating a skeleton framework and folder structure to place the thesis files in. The resulting template can be found on Sunil's site here: http://www.sunilpatel.co.uk/thesis-template.

Sunil's template was made available through [LaTeXTemplates](http://www.LaTeXTemplates.com) where it was modified many times based on user requests and questions. Version 2.0 and onwards of this template represents a major modification to Sunil's template and is, in fact, hardly recognisable. The work to make version 2.0 possible was carried out by Vel (vel@latextemplates.com)  and Johannes Böttcher.


## What this Template Includes

### Folders


* Appendices -- this is the folder where you put the appendices. Each appendix should go into its own separate qmd file. An example and template are included in the directory.

* Chapters -- this is the folder where you put the thesis chapters. Each chapter should go in its own separate qmd file.

* Figures -- this folder contains static figures for the thesis, i.e. figures that are not generated by code in the chapters.

### Files

* example.bib -- this is file that contains all the bibliographic information and references that you will be citing in the thesis for use with BibTeX. You can write it manually, but there are reference manager programs available that will create and manage it for you. Zotero is popular and integrates with RStudio IDE if you use that.

* MastersDoctoralThesis.cls -- this is the class file that tells \LaTeX{} how to format the thesis. 

* pdf in docs folder -- this is your typeset thesis.

* Frontmater folder -- this has the files for the various front matter elements.


## Bibliography and Citations

Citations will be added and formatted automatically for you.

If you use the RStudio IDE, then you can link Zotero to RStudio and Quarto will find your citations for you when you enter `@`. This is in the visual editor mode. Make sure to search for videos on how to do this as using Zotero libraries will make your citation and bibliography management much much easier.

In the text use `@smith2000` to produce Smith (2000) add use `[@smith2000, @jones1999]` to produce (Smith 2000; Jones 1999). See the natbib cheatsheet for how to do other types of formatting for your in text citations. The bibliography style (`classoption: "authoryear"`) is used for the bibliography and is a fully featured style that will even include links to where the referenced paper can be found online. 

#### A Note on bibtex

The bibtex backend used in the template by default does not correctly handle unicode character encoding (i.e. "international" characters). You may see a warning about this in the compilation log and, if your references contain unicode characters, they may not show up correctly or at all. One solution to this is to use the biber backend instead of the outdated bibtex backend. This is done by finding this in `tex/in-header.tex`: `backend=bibtex` and changing it to `backend=biber`. Google a bit to find information on this.









See the Quarto manual for full examples and instructions.

### Typesetting mathematics

If your thesis is going to contain heavy mathematical content, \LaTeX{} will make it look beautiful, for HTML or PDF output.

The [Not So Short Introduction to LaTeX](http://www.ctan.org/tex-archive/info/lshort/english/lshort.pdf) should tell you everything you need to know for most cases of typesetting mathematics. If you need more information, a much more thorough mathematical guide is available from the AMS called, [A Short Math Guide to LaTeX](http://tug.ctan.org/info/short-math-guide/short-math-guide.pdf).


## In Closing

Good luck and have lots of fun!

This guide was written originally by

Sunil Patel: http://www.sunilpatel.co.uk}{www.sunilpatel.co.uk

and Vel: http://www.LaTeXTemplates.com

and heavily shortened and adapted for [Quarto](https://quarto.org/) by [Eli Holmes](https://eeholmes.github.io).
